---
title: "TidyTemplate"
date: 2020-12-22
output: html_output
---

# TidyTuesday



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(countrycode)
library(patchwork)
library(ggtext)
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.
Its Big Mac

```{r Load}

tt <- tt_load("2020-12-22")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

bm <- tt$`big-mac`

bm$region <- countrycode::countrycode(bm$iso_a3,"iso3c","region")

bm[is.na(bm$region),]$region <- "Europe-EU"

bm %>% 
    filter(str_detect(str_to_lower(name),"united states")) %>% 
    View()

bm %>% select(name) %>% unique

bm %>% 
  filter(str_detect(str_to_lower(name),"states|india|thailand|euro")) %>%
  ggplot()+
  geom_point(aes(date,local_price))+
  geom_smooth(aes(date,local_price),se=FALSE,method = "lm",colour = "red")+
  facet_grid(rows = vars(region),scales = "free")

bm %>% 
  group_by(region,date) %>% 
  summarise(usd_raw = mean(usd_raw)) %>% 
  View()
  
bm_r <- bm %>% 
  filter(!str_detect(iso_a3,"USA|CAN")) %>% 
  group_by(region,date) %>% 
  summarise(usd_raw = mean(usd_raw))

mac_conch <- bm_r %>% 
  ggplot()+
  geom_line(data = bm %>% filter(!str_detect(iso_a3,"USA|CAN")),
             aes(date,usd_raw,group = iso_a3,color = region),alpha = 0.1,size = 1)+
    geom_point(data = bm %>% filter(!str_detect(iso_a3,"USA|CAN")),
             aes(date,usd_raw,group = iso_a3,color = region),alpha = 0.1,size = 1)+
  geom_smooth(aes(date,usd_raw,color = region),se=FALSE,method = "lm",size = 1.1)+
  scale_y_continuous()+
  scale_color_brewer(palette = "Dark2")+
  coord_polar()+
  xlab("")+ylab("")+
  labs(title = "**The Undervaluation Spiral**",
       subtitle = "All the regions of the world have a consistent trend of currency undervaluation <br> **The Mac Conch**",
       caption = "https://www.economist.com/bigmac
       visulaization by @rahulvilaskale")+
  theme_minimal()+
  theme(plot.title = element_markdown(hjust = 0.5),
        plot.subtitle = element_markdown(hjust = 0.5))+
  theme(legend.position = "left",legend.title = element_blank(),axis.line = element_blank())


  
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(plot = mac_conch,
  filename = "mac_conch.png",
  device = "png")

```
