---
title: "TidyTemplate"
date: 2020-08-29
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(RColorBrewer)
library(viridis)
theme_set(theme_light())

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-08-25")
tt

chopped <-tt$chopped

```

```{r}
library(glue)
chopped %>% 
  ggplot(aes(episode_rating)) +
  geom_histogram(bin =16)

 chopped_series <- chopped %>% 
  filter(!is.na(episode_rating)) %>% 
  group_by(season) %>% 
  mutate(season_avg = mean(episode_rating)) %>% 
  ungroup() %>% 
  mutate(select_episode_name = 
           case_when(
              episode_rating > 9 | episode_rating < 7 ~ glue("{season}.{season_episode}.{episode_name}"),
              TRUE ~ "")) %>%
  ggplot(aes(series_episode,episode_rating)) +
    geom_line(aes(color = factor(season)),alpha = 0.5) +
    geom_point(aes(color = factor(season))) +
    geom_line(aes(series_episode,season_avg),color = "black",alpha = 0.8) +
    ggrepel::geom_text_repel(aes(label = select_episode_name), 
              vjust="inward",hjust="inward", 
              force = 2,size = 3, alpha = 0.5) +
    theme(legend.position = "None")+
    labs(title = "Chopped episode ratings",
         subtitle = "Colors indicate different seasons. Black line is average rating / season",
         caption = "#TidyTuesday 2020 Week 35 dataset \nanalysis by @rahulvilaskale",
         x = "Series Episode", y = "Episode Rating")

chopped_series
```

# Play with ingredients
```{r}
ingredients <- chopped %>% 
  select(season:episode_rating,appetizer:dessert) %>% 
  pivot_longer(appetizer:dessert, names_to = "course", values_to = "ingredients") %>% 
  separate_rows(ingredients, sep = ",") %>% 
  mutate(ingredients = str_trim(ingredients))

ingredients %>% 
  mutate(ingredients = str_to_title(ingredients)) %>% 
  add_count(ingredients,sort = TRUE) %>% 
  filter(n>=10) %>% 
  mutate(ingredients = fct_reorder(ingredients,season)) %>% 
  ggplot(aes(season,ingredients, fill = n))+
  geom_boxplot()+
  theme(legend.title = element_blank(),
        legend.position = "right")+
  labs(title = "Popular Ingredients in Chopped",
       subtitle = "Atleast appeared 10 times in show, colors gives frequency",
       caption = "#TidyTuesday 2020 Week 35 dataset \nanalysis by @rahulvilaskale",
       x = "Seasons",
       y= "")+
  scale_fill_viridis(option = "D",alpha = 0.7,direction = -1)

```

