---
title: "TidyTemplate"
date: 2020-09-01
output: html_output
---

# TidyTuesday
This data set is of so exciting !!
I work with John Deere and tractors and agriculture is what i love.


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_minimal())


```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-09-01")
tt

tidy_tues_link <- "https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-09-01"
credit_data <- "https://ourworldindata.org/crop-yields"
key_crop_yields <- tt$key_crop_yields
arable_land <- tt$arable_land_pin
fertilizer <- tt$cereal_crop_yield_vs_fertilizer_application
land_use<- tt$land_use_vs_yield_change_in_cereal_production
tractor <- tt$cereal_yields_vs_tractor_inputs_in_agriculture

```

# Extra Data from fso 
Link "http://www.fao.org/faostat/en/#data/RL"
Gives details of land use.

```{r land_use_details}

library(gapminder)

# area in data is 1,000 Hectares which is 10 Square Kilometers
# multilpy by 10 at arrive at 1 sqkm

land_use_details <- read_csv("FAOSTAT_data_9-1-2020.csv",
                             col_types = cols(.default = col_character())) %>%
  janitor::clean_names() %>% 
  transmute(Entity = area,year = as.integer(year),land_category = item,area_sq_km = as.double(value)*10) %>% 
  mutate(land_category = fct_lump(land_category,7,other_level = "Other")) %>% 
  group_by(Entity,year,land_category) %>%
  summarise(area_sq_km = sum(area_sq_km)) %>% 
  ungroup() %>%
  arrange(Entity,year,desc(area_sq_km))%>% 
  pivot_wider(names_from = land_category,values_from = area_sq_km) %>% 
  janitor::clean_names()

country <- geonames::GNcountryInfo()

country_finance <- gapminder::gapminder %>% 
                      select(country,year,gdpPercap,pop) %>% 
                      left_join(gapminder::country_codes %>% select(country,iso_alpha), by=c("country"))

country_finance <- country_finance %>% 
                      filter(year >=1990 & year <=2000) %>% 
                      group_by(iso_alpha) %>% 
                      summarise(gdpPercap_mean = mean(gdpPercap))
                      


country_finance %>% ggplot()+
                        geom_histogram(aes(log(gdpPercap_mean)),bins = 35)
```

#ToDos
1. Custom theme and font - reproduce report as by our world in data
2. Learn interactive visualization


# Questions to ask?

1. Tractors potential for growth in no. of tractors? 
2. Mechanization potential?
3. Yield growths ? can they be explained by mechanization and fertilizer use ?
4. Population growth; does the growth rate match with yield increase ?


# Lets start with visualization

```{r explore tractor}
library(viridis)
library(RColorBrewer)
library(lubridate)
library(scales)


trac <- tractor %>%
  janitor::clean_names() %>% 
  mutate(year = as.integer(year)) %>% 
  rename(trac_density = tractors_per_100_sq_km_arable_land) %>% 
  filter(!is.na(trac_density),!is.na(year)) %>% 
  left_join((land_use_details %>% select(entity,year,arable_land)), by = c("entity","year")) %>% 
  left_join(country %>% select(isoAlpha3,continentName),by = c("code" = "isoAlpha3")) %>%
  mutate(qty = trac_density*arable_land/100) %>% #as density is per 100 sq km
  filter(!is.na(qty),!is.na(continentName), year <=2000,year >=1990) %>% 
  arrange(year) %>% 
  group_by(continentName,year) %>% 
  summarise(qty = round(sum(qty)/10^6,2)) %>%
  transmute(continentName,year,qty) %>%
  mutate(year =  lubridate::ymd(paste(year,"01","01",sep = "-"))) %>% 
  arrange(desc(year),continentName) %>% 
  ungroup()

trac %>%
  mutate(year_number = year(year)) %>% 
  group_by(year) %>% 
  mutate(prop_percent = qty / sum(qty)) %>%
  filter(prop_percent >=0.01) %>% 
  ggplot(aes(year,prop_percent,fill = fct_reorder(continentName,prop_percent)))+
  geom_area(alpha = 0.7,
            color = "grey")+
  geom_text(aes(label = percent(prop_percent,accuracy = 1)),
            position = position_fill((vjust = 0.5)),
            size=3.5,
            color = "black",
            alpha = 0.8)+
  theme_minimal()+
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text( size = 10))+
  labs(title = "Tractor population share among continents",
       subtitle = "Years: 1990 - 2000",
       caption = paste0("Source: ",credit_data,"\nVisual: @rahulvilaskale"))+
  scale_x_date(date_breaks = "1 years",name = NULL, date_labels = "%Y")+
  scale_y_continuous(name = NULL,labels = NULL)+
  scale_fill_brewer(palette = "Set3")


```

```{r model}

```


```{r explore potential}

library(ggrepel)

tractor %>%
  janitor::clean_names() %>% 
  mutate(year = as.integer(year)) %>% 
  rename(trac_density = tractors_per_100_sq_km_arable_land,
         cereal_density = cereal_yield_kilograms_per_hectare_kg_per_hectare) %>% 
  filter(!is.na(trac_density),!is.na(year)) %>% 
  left_join((land_use_details %>% select(entity,year,arable_land)), by = c("entity","year")) %>% 
  left_join(country %>% select(isoAlpha3,continentName),by = c("code" = "isoAlpha3")) %>%
  mutate(qty = trac_density*arable_land/100) %>% 
  filter(!is.na(qty),!is.na(continentName), year <=2000,year >=1990) %>% 
  mutate(year =  lubridate::ymd(paste(year,"01","01",sep = "-"))) %>% 
  mutate(selected_countries = if_else(
                                  ( log(cereal_density) < 8 &
                                    log(trac_density) <= 4 &
                                    log(arable_land) > 10),
                                  entity,
                                  NA_character_))%>%
  group_by(code,selected_countries,continentName) %>% 
  summarise(cereal_density = mean(cereal_density),
            trac_density = mean(trac_density),
            total_population_gapminder = mean(total_population_gapminder),
            arable_land = mean(arable_land)) %>% 
  left_join(country_finance, by = c("code" = "iso_alpha")) %>% 
  ggplot(aes(log(cereal_density),log(trac_density)))+
    geom_smooth(method = "lm",se = FALSE,color = "grey",alpha = 0.9)+
    geom_point(aes(color = fct_reorder(continentName,-trac_density),size = arable_land))+
    geom_text_repel(aes(label = selected_countries))+
    theme_minimal()+
    theme(legend.title = element_blank())+
    guides(size=FALSE)+
    labs(title = "Mechanization Improves Yield",
         subtitle = "Average cereal yeilds vs. Average tractor density. Larger dots - higher arable land.\nCountries with high mechanization potential are highlighted, (higher arable area but lower tractor desnsity and lower cereal yield.)",
         caption = paste0("Source: ",credit_data,"\nVisual: @rahulvilaskale"))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_continuous(name = "Cereal Yield - log scale")+
  scale_y_continuous(name = "Tractor Density - log scale")



```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}



```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
